### 2024-10-07 esop25/ipj.tex
checkpoint

\begin{definition}
  Given $H,C$ and $\prog$ with $\views(\prog) = V$ and $\secrets(\prog) = S$,
  $\adversary$, and $\store \in \aruns(\prog)$, we say $\store$ is
  \emph{abberant} if $\neg\exists \store' \in \runs(\prog) .
  \store_{S_H \cup V} = \store'_{S_H \cup V}$, and if
   $\neg\exists \store' \in \runs(\prog) .
  \store_{S_H \cup \{ x \}} = \store'_{S_H \cup \{ x \}}$ we say
  any $x \in V$ \emph{has an abberation}.
\end{definition}

\begin{lemma}
  If $\prog$ does not have integrity for some $H,C$, then it has
  abberant $\store \in \aruns(\prog)$ for some $\adversary$. 
\end{lemma}

\begin{lemma}
  Given pre-processing predicate $\eqspre$ and protocol $\prog$ with
  $\views(\prog) = V$, if 
  $\ipj{\eqs}{\prog}{\Delta}$ is valid
  and $x\in V$ has an abberation for some $H,C$,
  then $\cheatj{\Delta}{H,C}{\seclev}$ and $\seclev(x) = \lolab$.
\end{lemma}

>>>>

\begin{definition}
  Given $H,C$ and $\prog$ with $\views(\prog) = V$ and $\secrets(\prog) = S$,
  $\adversary$, and $\store \in \aruns(\prog)$, we say $\store$ is
  \emph{aberrant through $V' \subseteq V$} if $\neg\exists \store' \in \runs(\prog) .
  \store_{S_H \cup V'} = \store'_{S_H \cup V'}$, and if there exists
  such $\adversary$ and $\store$ we say any
  $x \in V'$ is \emph{in an aberration}.
\end{definition}

\begin{lemma}
  If $\prog$ does not have integrity for some $H,C$, then it has
  aberrant $\store \in \aruns(\prog)$ for some $\adversary$. 
\end{lemma}

\begin{lemma}
  Given $\prog$ and $H,C$, if $x$ is in an aberration then one of
  the two inductively defined conditions holds:
  \begin{enumerate}[\hspace{5mm}i.]
  \item There exists $\xassign{x}{\be}{\cid} \in \prog$ with $\cid \in C$.
  \item There exists $\xassign{x}{\be}{\cid} \in \prog$ with $\cid \in H$ and
    $x' \in \vars(\be)$ such that $x'$ is in an aberration.
  \end{enumerate}
\end{lemma}

\begin{lemma}
  Given pre-processing predicate $\eqspre$ and protocol $\prog$ with
  $\views(\prog) = V$, if 
  $\ipj{\eqs}{\prog}{\Delta}$ is valid
  and $x\in V$ has an aberration for some $H,C$,
  then $\cheatj{\Delta}{H,C}{\seclev}$ and $\seclev(x) = \lolab$.
\end{lemma}
